
```{r importdata, echo=FALSE}
drake::loadd(tracks)
drake::loadd(track_points)
drake::loadd(c(loc_data, site_data))

# test <- pull_data(sheet = try)

```


---
output: 
  html_document:
    self_contained: true 
 
params:
  set_title: "My Title!"
title: "Parsnip Watershed Fish Habitat Confirmations"
date: "`r format(Sys.time(), '%B %Y')`"
---


```{r setup, include = TRUE, echo =FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, 
                      fig.align="center", fig.width = 5.118, fig.height = 3.409,
                      fig.path = ('fig/'))

##this is from our title if we want it to autogenerate "Fish Habitat confirmation - PSCIS Crossing `r my_site` - `r pull_data(sheet = loc_data, site = my_site)`"
```


```{r include = FALSE,  message=FALSE}

plot <- drake::r_vis_drake_graph(main = 'Interactive Drake Workflow Graph Showing Project Structure and Dependencies')
```


```{r}
# test <- pull_data(sheet = loc_data, site = my_site)

```


```{r}
##need to get basic information
#road name
#tenure holder
#order
#watershed area
#mainstem length
#name stream flows into
#distance from the downstream confluence to the crossing
#fish species known in the stream
#fish species known in downstream system
#amount of habitat upstream of the crossing
#table of the type of habitat upstream
#table of habitat characteristics upstream and downstream

```

# Restoration Candidates {.tabset}

## Overview

```{r}
loadd(table)

names_table <- tibble(old_names = names(table),
                      new_names = c('alias_local_name', 'Site', 'Location', 'Zone (UTM)',
                                    'Easting', 'Northing',
                                    'Stream', 'Channel Width (m)', 'Wetted Width (m)',
                                    'Pool depth (m)','Bankfull Depth (m)', 'Gradient (%)',
                                    'Substrate (dom)', 'Substrate (subdom)', 'Feature',
                                    'utm_zone', 'utm_easting', 'utm_northing'))
```


```{r}
##make habitat table

names_hab_table <- c('alias_local_name', 'site', 'location', 'gazetted_names','avg_channel_width_m',
         'avg_wetted_width_m', 'average_residual_pool_depth_m',
         'average_bankfull_depth_m','average_gradient_percent',
         'bed_material_dominant', 'bed_material_subdominant')


table_hab <- table %>%
  dplyr::select(all_of(names_hab_table)) 

```



```{r makeoverview}

names_overview_table <- c('alias_local_name', 'site', 'location', 'gazetted_names','zone', 
                          'easting', 'northing')


table_overview <- table %>%
  dplyr::select(all_of(names_overview_table)) %>%  
  purrr::set_names(., nm = dplyr::pull(
  left_join(as_tibble_col(names_overview_table, column_name = 'old_names'),
               names_table, by = 'old_names'),
            new_names)) %>% 
  select(-alias_local_name) 


##clean up the site_id column of our priorities so we can join to the overview table
priorities <- drake::readd(priorities) %>% 
  tidyr::separate(site_id, into = c('site', 'location'), remove = F)

table_overview <- left_join(
  table_overview, 
  select(priorities,
         site, location, length_surveyed = length, priority, comments),
  by = c('Site' = 'site','Location' = 'location')
) %>%
  select(Site, Stream, Location:Northing, everything())

##add the name of the road and the tenure holder from our pscis sheet
table_overview <-  left_join(table_overview,
                              select(drake::readd(pscis),
                              pscis_crossing_id, road_name, road_tenure),
                              by = c('Site' = 'pscis_crossing_id')) %>% 
  # filter(priority %ilike% 'high') %>% 
  # select(Site, Stream, Location, road_name, road_tenure, everything()) %>% 
  mutate(Location = case_when(Location == 'ds' ~ 'Downstream',
                             TRUE ~ 'Upstream'))

##add the modelled fish habitat from the fish habitat model output
table_overview <- left_join(
  table_overview %>% mutate(site_integer = as.integer(Site)),
  select(drake::readd(fish_habitat_info),
                     pscis_stream_crossing_id, uphab_gross_sub22, upstr_species),
         by =  c('site_integer' = 'pscis_stream_crossing_id'), 
  na_matches = "never") %>% ##nice little trick
  mutate(uphab_gross_sub22 = round(uphab_gross_sub22/1000, 2)) %>% 
  arrange((site_integer), desc(Location)) %>% 
  select(Site, Stream, Location, 'Zone (UTM)', 'Easting', 'Northing',
         road_name, road_tenure, upstr_species, uphab_gross_sub22, everything()) 
```


```{r}

table_overview_prep <- table_overview %>% 
  rename(`Road Name` = road_name, `Road Responsibility` = road_tenure,
         Priority = priority, Comments = comments, `Habitat Modelled (m)` = uphab_gross_sub22,
         Species = upstr_species) %>% 
  select(-site_integer)


DT::datatable(
  table_overview_prep,
  caption = 'Table 1: Overview of Parsnip River Watershed Crossings Assessed with Habitat Confirmations.',
  rownames = FALSE,
    options = list(columnDefs = list(list(
    targets = ncol(table_overview_prep)-1, 
    render = JS(
      "function(data, type, row, meta) {",
      "return type === 'display' && data.length > 20 ?",
      "'<span title=\"' + data + '\">' + data.substr(0, 20) + '...</span>' : data;",
      "}")
  ))))

# names(hab_table) <- pull(table_names, new_names)  

# ##make the hab table for the memo
# table_memo <- table %>% 
#   select(-utm_zone, -utm_easting, -utm_northing)


  # filter(local_name == paste0(my_site, '_us')) %>% 
  # t() %>% 
  # as_tibble()
#   filter(local_name %ilike% my_site) %>% 

# local_name, 
#          avg_channel_width_m, 
#          avg_wetted_width_m,
#          )

```


## Habitat Summaries

```{r}

table_hab_prep <- table_hab %>% 
  purrr::set_names(., nm = dplyr::pull(
    dplyr::filter(names_table, 
                  old_names %in% names_hab_table), 
    new_names)) %>% 
   mutate(Location = case_when(Location == 'ds' ~ 'Downstream',
                             TRUE ~ 'Upstream')) %>% 
  select(-alias_local_name)


DT::datatable(
  table_hab_prep,
  caption = 'Table 2: Summary of Habitat for Parsnip River Watershed Habitat Confirmations.',
  rownames = FALSE,
    options = list(columnDefs = list(list(
    targets = ncol(table_hab_prep)-1, 
    render = JS(
      "function(data, type, row, meta) {",
      "return type === 'display' && data.length > 20 ?",
      "'<span title=\"' + data + '\">' + data.substr(0, 20) + '...</span>' : data;",
      "}")
  ))))

```




```{r }

##Set up for the leaflet map with tracks and track points loaded within the same chunk.  All the packages, functions and plan for data targets is detailed in our .R/ folder.
##here are the indexes of the points
drake::loadd(my_tracks, tracks_of_points)



##move this to the plan
##!!!!!!!!!!!need to change the name of track 57687 in the gpx!!!!!!!!!!!!
# track_point_idx_list <- sf::st_intersects(tracks, track_points) %>% 
#   purrr::set_names(., nm = pull(tracks, name))
# 
# tracks_of_points <- lapply(track_point_idx_list, 
#                            make_tracks_of_points, track_points = track_points)
# 
# 
# my_tracks <- tracks_of_points %>% 
#   # keep(names(.) %like% my_site) %>% 
#   map(points2line_trajectory)  ##convert our points to lines
# 
# # names(my_tracks)
# # addPolylines_multi <- function(x){
# #     addPolylines(data=x,  opacity=1, color = 'red',
# #                    fillOpacity = 0.75, weight=2)
# # }
# 
# #clean up workspace
# rm(track_point_idx_list
#    # , tracks_of_points
#    )
```

## High Priority Crossings {.tabset}

### PSCIS 125000 
```{r}
my_site <- '125000'
```


This is a start on a semi-automated write-up for each of the crossings built from our source files.  
PSCIS crossing `r my_site` is located on "link to source" rd, UTM:`r pull_utm(sheet = loc_data, site = my_site)`.

```{r}

DT::datatable(
  filter(table_overview_prep,
         Site == my_site),
  caption = 'Table 3: Summary of Habitat for Parsnip River Watershed Habitat Confirmations.',
  rownames = FALSE,
    options = list(columnDefs = list(list(
    targets = ncol(table_hab_prep)-1, 
    render = JS(
      "function(data, type, row, meta) {",
      "return type === 'display' && data.length > 20 ?",
      "'<span title=\"' + data + '\">' + data.substr(0, 20) + '...</span>' : data;",
      "}")
  ))))
# knitr::kable(
#   table_overview %>% filter(Site %like% my_site)
#   )



# knitr::kable(
#   table_hab %>% filter(Site %like% my_site)
#   )
```

```{r}
DT::datatable(
  filter(table_hab_prep,
         Site == my_site),
  caption = paste0('Summary of Habitat for PSCIS Crossing #', my_site, '.'),
  rownames = FALSE,
    options = list(columnDefs = list(list(
    targets = ncol(table_hab_prep)-1, 
    render = JS(
      "function(data, type, row, meta) {",
      "return type === 'display' && data.length > 20 ?",
      "'<span title=\"' + data + '\">' + data.substr(0, 20) + '...</span>' : data;",
      "}")
  ))))
```


```{r}
photoPoints <- read.csv(file = 'data/photos/photo_metadata.csv')
# remove photos with no coordinates
photoPoints <- photoPoints[!is.na(photoPoints$lat_map),]

photoPoints$url <- as.character (photoPoints$url)
photoPoints
```

```{r map, out.width = '100%'}
##--------lets map it-----------------------------------------------------------------------
##time to set the watershed code here
##pass it get the watershed boundaries. Dissolve boundaries and display semi-transparent.
##add a culvert measurements output table with all the usual photos
##georeference the upstream and downstream photos from the camera by cross-referencing the time to the gps.


map <- leaflet() %>%
  leaflet(height=500, width=500) %>% 
  addTiles() %>%
    addMouseCoordinates(proj4 = 26911) %>% ##can't seem to get it to render utms yet

  addProviderTiles("Esri.WorldImagery", group = "ESRI Aerial") %>% 
  addProviderTiles("Esri.WorldTopoMap", group = "Topo") %>%
  # addMeasure() %>% 
    # setView(lng = -105.644, lat = 51.618, zoom = 3) 
  addPolylines(data=my_tracks$`125000_us_track1`,  opacity=1, color = 'red',
                   fillOpacity = 0.75, weight=2) %>%
  addPolylines(data=my_tracks$`125000_ds_track`,  opacity=1, color = 'red',
               fillOpacity = 0.75, weight=2) %>%

  addMarkers(lng = photoPoints$lon_map,lat = photoPoints$lat_map, popup = popupImage(photoPoints$url, src = "remote")) %>% 

  addLayersControl(
    baseGroups = c("ESRI Aerial", "Topo"),
    overlayGroups = c(my_tracks$`125000_ds_track`),
    options = layersControlOptions(collapsed = F)) %>% 
  
    addMiniMap(tiles = providers$"Esri.WorldTopoMap",
             zoomLevelOffset = -6)    # setView(lng = -105.644, lat = 51.618, zoom = 3) ##this becomes the latest and greatest pscis crossing utm
map
```

### PSCIS 125180
```{r}
my_site <- '125180'
```

```{r}
DT::datatable(
  filter(table_hab_prep,
         Site == my_site),
  caption = paste0('Summary of Habitat for PSCIS Crossing #', my_site, '.'),
  rownames = FALSE,
    options = list(columnDefs = list(list(
    targets = ncol(table_hab_prep)-1, 
    render = JS(
      "function(data, type, row, meta) {",
      "return type === 'display' && data.length > 20 ?",
      "'<span title=\"' + data + '\">' + data.substr(0, 20) + '...</span>' : data;",
      "}")
  ))))
```



```{r map2}
##--------lets map it-----------------------------------------------------------------------
##easybutton info  https://rstudio.github.io/leaflet/morefeatures.html
map <- leaflet() %>%
  leaflet(height=500, width=500) %>% 
  addTiles() %>%
    addMouseCoordinates(proj4 = 26911) %>% ##can't seem to get it to render utms yet

  addProviderTiles("Esri.WorldImagery", group = "ESRI Aerial") %>% 
  addProviderTiles("Esri.WorldTopoMap", group = "Topo") %>%
  # addMeasure() %>% 
    # setView(lng = -105.644, lat = 51.618, zoom = 3) 
  addPolylines(data=my_tracks$`125180_us`,  opacity=1, color = 'red',
                   fillOpacity = 0.75, weight=2) %>%
  addPolylines(data=my_tracks$`125180_ds`,  opacity=1, color = 'red',
               fillOpacity = 0.75, weight=2) %>%
  
  addLayersControl(
    baseGroups = c("ESRI Aerial", "Topo"),
    overlayGroups = c(my_tracks$`125000_ds_track`),
    options = layersControlOptions(collapsed = F)) %>% 
  addMiniMap(tiles = providers$"Esri.WorldTopoMap",
             zoomLevelOffset = -6)    # setView(lng = -105.644, lat = 51.618, zoom = 3) ##this becomes the latest and greatest pscis crossing utm
map




```



## Workflow Layout
parsnip_habitat_assessment.xls is the [Fish Data Submission Spreadsheet Template - V 2.0, April 16, 2019 ](https://www2.gov.bc.ca/gov/content/environment/plants-animals-ecosystems/fish/fish-and-fish-habitat-data-information/fish-data-submission/submit-fish-data#submitfish).  


```{r out.width = '100%'}
plot
```

