
```{r importdata, echo=FALSE}
drake::loadd(tracks)
drake::loadd(track_points)
drake::loadd(c(loc_data, site_data))

# test <- pull_data(sheet = try)

```


---
output: 
  html_document:
    self_contained: true 
 
params:
  set_title: "My Title!"
title: "Parsnip Watershed Fish Habitat Confirmations - DRAFT"
date: "`r format(Sys.time(), '%B %Y')`"
---


```{r setup, include = TRUE, echo =FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, 
                      fig.align="center", fig.width = 5.118, fig.height = 3.409,
                      fig.path = ('fig/'))

##this is from our title if we want it to autogenerate "Fish Habitat confirmation - PSCIS Crossing `r my_site` - `r pull_data(sheet = loc_data, site = my_site)`"
```


```{r include = FALSE,  message=FALSE}

plot <- drake::r_vis_drake_graph(main = 'Interactive Drake Workflow Graph Showing Project Structure and Dependencies')
```


```{r}
# test <- pull_data(sheet = loc_data, site = my_site)

```


```{r}
##need to get basic information
#road name
#tenure holder
#order
#watershed area
#mainstem length
#name stream flows into
#distance from the downstream confluence to the crossing
#fish species known in the stream
#fish species known in downstream system
#amount of habitat upstream of the crossing
#table of the type of habitat upstream
#table of habitat characteristics upstream and downstream

```

# Restoration Candidates {.tabset}

## Overview

```{r}
loadd(table)

names_table <- tibble(old_names = names(table),
                      new_names = c('alias_local_name', 'Site', 'Location', 'Zone (UTM)',
                                    'Easting', 'Northing',
                                    'Stream', 'Channel Width (m)', 'Wetted Width (m)',
                                    'Pool depth (m)','Bankfull Depth (m)', 'Gradient (%)',
                                    'Substrate (dom)', 'Substrate (subdom)', 'Feature',
                                    'utm_zone', 'utm_easting', 'utm_northing'))
```


```{r loadpriorities}
##clean up the site_id column of our priorities so we can join to the overview table
priorities <- drake::readd(priorities) %>% 
  tidyr::separate(site_id, into = c('site', 'location'), remove = F)

```



```{r loadoverview}

names_overview_table <- c('alias_local_name', 'site', 'location', 'gazetted_names','zone', 
                          'easting', 'northing')


table_overview <- table %>%
  dplyr::select(all_of(names_overview_table)) %>%  
  purrr::set_names(., nm = dplyr::pull(
  left_join(as_tibble_col(names_overview_table, column_name = 'old_names'),
               names_table, by = 'old_names'),
            new_names)) %>% 
  select(-alias_local_name) 



table_overview <- left_join(
  table_overview, 
  select(priorities,
         site, location, length_surveyed = length, hab_value, priority, comments),
  by = c('Site' = 'site','Location' = 'location')
) %>%
  select(Site, Stream, Location:Northing, everything())

##add the name of the road and the tenure holder from our pscis sheet
table_overview <-  left_join(table_overview,
                              select(drake::readd(pscis),
                              pscis_crossing_id, road_name, road_tenure),
                              by = c('Site' = 'pscis_crossing_id')) %>% 
  # filter(priority %ilike% 'high') %>% 
  # select(Site, Stream, Location, road_name, road_tenure, everything()) %>% 
  mutate(Location = case_when(Location == 'ds' ~ 'Downstream',
                             TRUE ~ 'Upstream'))

##add the modelled fish habitat from the fish habitat model output
table_overview <- left_join(
  table_overview %>% mutate(site_integer = as.integer(Site)),
  select(drake::readd(fish_habitat_info),
                     pscis_stream_crossing_id, uphab_gross_sub22, upstr_species),
         by =  c('site_integer' = 'pscis_stream_crossing_id'), 
  na_matches = "never") %>% ##nice little trick
  mutate(uphab_gross_sub22 = round(uphab_gross_sub22/1000, 1)) %>% 
  arrange((site_integer), desc(Location)) %>% 
  select(Site,  Stream, road_name, Location, 'Zone (UTM)', 'Easting', 'Northing',
         road_tenure, upstr_species, uphab_gross_sub22, everything()) 
```


```{r}

table_overview_prep <- table_overview %>% 
  filter(Location == 'Upstream' ) %>% 
  mutate(upstr_species = as.character(upstr_species),
         upstr_species = case_when(Site %like% '125000' ~ 'RB, CC',
                             Site %like% '57690' ~ 'RB',
                             Site %like% 'CV1' ~ 'BT',
                             Site %like% '125345' ~ '(RB), CC',
                             TRUE ~ upstr_species),
         road_name = case_when(Site %like% 'CV1' ~ 'CN Railway',
                          Site %like% '57681' ~ 'CN Railway',
                             TRUE ~ road_name),
         `UTM (10N)` = paste0(Easting, " ", Northing),
         road_tenure = str_to_title(road_tenure),
         road_tenure = str_replace_all(road_tenure, 'Dmpg', 'FLNRORD'),
         upstr_species = str_replace_all(upstr_species, ',', ', '),
         priority = fct_relevel(priority, levels = 'High', 'Moderate', 'Low')) %>% 
  
  select(Site, Stream, `Road` = road_name, Tenure = road_tenure, `UTM (10N)`, 
         `Fish Species` = upstr_species, `Habitat Gain (km)` = uphab_gross_sub22, `Habitat Value` = hab_value, Priority = priority, Comments = comments, -site_integer, -Location, -'Zone (UTM)', -'Easting', -'Northing') %>% 
  arrange(Priority, Site)
  
  


# DT::datatable(
#   table_overview_prep,
#   caption = 'Table 1: Overview of Parsnip River Watershed Crossings Assessed with Habitat Confirmations.',
#   rownames = FALSE,
#     options = list(columnDefs = list(list(
#     targets = ncol(table_overview_prep)-1, 
#     render = JS(
#       "function(data, type, row, meta) {",
#       "return type === 'display' && data.length > 20 ?",
#       "'<span title=\"' + data + '\">' + data.substr(0, 20) + '...</span>' : data;",
#       "}") 
#     
#       
#   )))) %>% 
#     formatStyle(columns = colnames(table_overview_prep), `font-size` = '10px')

filter(table_overview_prep) %>%
  gt::gt() %>% 
  cols_width(
    vars(Comments) ~ px(300),
    vars(`Habitat Gain (km)`) ~ px(70),
    everything() ~ px(60)
  ) %>% 
  tab_options(table.font.size = 11) %>% 
  tab_footnote(
    footnote = 'Habitat gain modelled based on Fish Habitat Model with 22% gradient threshold for "fish habitat".',
    locations =  cells_column_labels(
      columns = vars(`Habitat Gain (km)`)))


# names(hab_table) <- pull(table_names, new_names)  

# ##make the hab table for the memo
# table_memo <- table %>% 
#   select(-utm_zone, -utm_easting, -utm_northing)


  # filter(local_name == paste0(my_site, '_us')) %>% 
  # t() %>% 
  # as_tibble()
#   filter(local_name %ilike% my_site) %>% 

# local_name, 
#          avg_channel_width_m, 
#          avg_wetted_width_m,
#          )

```


```{r loadhabitat}
##make habitat table

names_hab_table <- c('alias_local_name', 'site', 'location', 'gazetted_names','avg_channel_width_m',
         'avg_wetted_width_m', 'average_residual_pool_depth_m',
         'average_bankfull_depth_m','average_gradient_percent',
         'bed_material_dominant', 'bed_material_subdominant')


table_hab <- table %>%
  dplyr::select(all_of(names_hab_table)) 

table_hab <- left_join(
  table_hab, 
  select(priorities,
         site, location, length_surveyed = length, priority, comments),
  by = c('site','location')
)
  # select(Site, Stream, Location:Northing, everything())

```


```{r makehabtable}
new_names <-  c('alias_local_name', 'Site', 'Location', 
                'Stream', 'Channel Width (m)', 'Wetted Width (m)',
                'Pool depth (m)','Bankfull Depth (m)', 'Gradient (%)',
                'Substrate (dominant)', 'Substrate (subdominant)', 'Length Surveyed (m)',
                'Priority', 'Comments')


table_hab_prep <- table_hab %>% 
  purrr::set_names(., nm = new_names) %>% 
   mutate(Location = case_when(Location == 'ds' ~ 'Downstream',
                             TRUE ~ 'Upstream')) %>% 
  select(-alias_local_name, -Stream)
```





## High Priority Crossings {.tabset}


```{r loadmapdata}
loadd(photo_metadata, my_tracks, tracks_of_points)
```


```{r}
# remove photos with no coordinates
photo_metadata <- photo_metadata[!is.na(photo_metadata$lat_map),]

photo_metadata$url <- as.character(photo_metadata$url)
```


### Chuchinka-Arctic FSR {.tabset}


```{r site125000}
#### Tributary to Parsnip River - PSCIS 125000 
my_site <- '125000'
```


```{r}
photo_metadata_site <- photo_metadata %>% 
  filter(crossing_id == my_site)


# This is a start on a semi-automated write-up for each of the crossings built from our source files.  
# PSCIS crossing `r my_site` is located on "link to source" rd, UTM:`r pull_utm(sheet = loc_data, site = my_site)`.
```


<br>

```{r}
filter(table_overview_prep,
         Site == my_site) %>%
  select(-Comments) %>% 
  gt::gt() %>% 
  tab_header(title="Overview") %>%
  cols_width(
    # vars(Comments) ~ px(300),
    # vars(`Habitat Gain (km)`) ~ px(70),
    everything() ~ px(90)
  ) %>% 
  tab_options(table.font.size = 11) %>% 
  tab_footnote(
    footnote = 'Habitat gain modelled based on Fish Habitat Model with 22% gradient threshold for "fish habitat".',
    locations =  cells_column_labels(
      columns = vars(`Habitat Gain (km)`)))

##DT table is a bit finicky for now
# DT::datatable(
#   filter(table_overview_prep,
#          Site == my_site),
#   rownames = FALSE
#   # options = list(columnDefs = list(list(
#   # targets = ncol(table_overview_prep)-1, 
#   # render = JS(
#   #   "function(data, type, row, meta) {",
#   #   "return type === 'display' && data.length > 20 ?",
#   #   "'<span title=\"' + data + '\">' + data.substr(0, 20) + '...</span>' : data;",
#   #   "}")))
# )

```

<br>

```{r}
filter(table_hab_prep, Site == my_site) %>%
  gt::gt() %>% 
  tab_header(title="Habitat Summary") %>% 
  cols_width(
    vars(Comments) ~ px(250),
    vars(`Substrate (dominant)`,`Substrate (subdominant)`) ~ px(75),
    vars(Location) ~ px(60),
    everything() ~ px(50)
  ) %>% 
  tab_options(table.font.size = 11) 


# DT::datatable(
#   table_hab_prep,
#   caption = 'Table 2: Summary of Habitat for Parsnip River Watershed Habitat Confirmations.',
#   rownames = FALSE,
#     options = list(columnDefs = list(list(
#     targets = ncol(table_hab_prep)-1, 
#     render = JS(
#       "function(data, type, row, meta) {",
#       "return type === 'display' && data.length > 20 ?",
#       "'<span title=\"' + data + '\">' + data.substr(0, 20) + '...</span>' : data;",
#       "}")
#   ))))
# 
# DT::datatable(
#   filter(table_hab_prep,
#          Site == my_site),
#   caption = paste0('Summary of Habitat for PSCIS Crossing #', my_site, '.'),
#   rownames = FALSE,
#     options = list(columnDefs = list(list(
#     targets = ncol(table_hab_prep)-1, 
#     render = JS(
#       "function(data, type, row, meta) {",
#       "return type === 'display' && data.length > 20 ?",
#       "'<span title=\"' + data + '\">' + data.substr(0, 20) + '...</span>' : data;",
#       "}")
#   ))))
```

<br>

#### Map


```{r out.width= '100%'}
##--------lets map it-----------------------------------------------------------------------
##time to set the watershed code here
##pass it get the watershed boundaries. Dissolve boundaries and display semi-transparent.
##add a culvert measurements output table with all the usual photos
##georeference the upstream and downstream photos from the camera by cross-referencing the time to the gps.


map <- leaflet() %>%
  leaflet(height=500, width=780) %>% 
  addTiles() %>%
    addMouseCoordinates(proj4 = 26911) %>% ##can't seem to get it to render utms yet

  addProviderTiles("Esri.WorldImagery", group = "ESRI Aerial") %>% 
  addProviderTiles("Esri.WorldTopoMap", group = "Topo") %>%
  # addMeasure() %>% 
    # setView(lng = -105.644, lat = 51.618, zoom = 3) 
  addPolylines(data=my_tracks$`125000_us_track1`,  opacity=1, color = 'red',
                   fillOpacity = 0.75, weight=2) %>%
  addPolylines(data=my_tracks$`125000_ds_track`,  opacity=1, color = 'red',
               fillOpacity = 0.75, weight=2) %>%
  addAwesomeMarkers(lng = photo_metadata_site$lon_map,lat = photo_metadata_site$lat_map,
             popup = popupImage(photo_metadata_site$url, src = "remote"),
clusterOptions = markerClusterOptions(),
label = paste0(photo_metadata_site$crossing_id, '_', photo_metadata_site$filename)) %>%
  addLayersControl(
    baseGroups = c("ESRI Aerial", "Topo"),
    # overlayGroups = c(my_tracks$`125000_ds_track`),
    options = layersControlOptions(collapsed = F)) %>% 
  
    addMiniMap(tiles = providers$"Esri.WorldTopoMap",
             zoomLevelOffset = -6)    # setView(lng = -105.644, lat = 51.618, zoom = 3) ##this becomes the latest and greatest pscis crossing utm
map
```

<br>

### Chuchinka-Missinka FSR  {.tabset}



```{r}
##this is doing nothing right now
# my_site <- '125179'
#### Tributary to Missinka River - PSCIS 125179
```


```{r}
photo_metadata_site <- photo_metadata %>% 
  filter(crossing_id %in% c('125179', '125180', '125186'))
```

<br>

```{r}
filter(table_overview_prep,
         Site %in% c('125179', '125180', '125186')) %>%
  select(-Comments) %>% 
  gt::gt() %>% 
  tab_header(title="Overview") %>%
  cols_width(
    # vars(Comments) ~ px(300),
    # vars(`Habitat Gain (km)`) ~ px(70),
    everything() ~ px(90)
  ) %>% 
  tab_options(table.font.size = 11) %>% 
  tab_footnote(
    footnote = 'Habitat gain modelled based on Fish Habitat Model with 22% gradient threshold for "fish habitat".',
    locations =  cells_column_labels(
      columns = vars(`Habitat Gain (km)`)))

```

<br>

```{r}
filter(table_hab_prep, 
       Site %in% c('125179', '125180', '125186')) %>%
  gt::gt() %>% 
  tab_header(title="Habitat Summary") %>% 
  cols_width(
    vars(Comments) ~ px(250),
    vars(`Substrate (dominant)`,`Substrate (subdominant)`) ~ px(75),
    vars(Location) ~ px(60),
    everything() ~ px(50)
  ) %>% 
  tab_options(table.font.size = 11) 

```

<br>

#### Map

```{r out.width= '100%'}
##--------lets map it-----------------------------------------------------------------------
##time to set the watershed code here
##pass it get the watershed boundaries. Dissolve boundaries and display semi-transparent.
##add a culvert measurements output table with all the usual photos
##georeference the upstream and downstream photos from the camera by cross-referencing the time to the gps.


map <- leaflet() %>%
  leaflet(height=500, width=780) %>% 
  addTiles() %>%
  addMouseCoordinates(proj4 = 26910) %>% ##can't seem to get it to render utms yet
  
  addProviderTiles("Esri.WorldImagery", group = "ESRI Aerial") %>% 
  addProviderTiles("Esri.WorldTopoMap", group = "Topo") %>%
  # addMeasure() %>% 
  # setView(lng = -105.644, lat = 51.618, zoom = 3)
  addPolylines(data=my_tracks$`125179_us_track`,  opacity=1, color = 'red',
               fillOpacity = 0.75, weight=2) %>%
  addPolylines(data=my_tracks$`125179_ds_track`,  opacity=1, color = 'red',
               fillOpacity = 0.75, weight=2) %>%
  addPolylines(data=my_tracks$`125180_ds`,  opacity=1, color = 'red',
               fillOpacity = 0.75, weight=2) %>%
  addPolylines(data=my_tracks$`125180_us`,  opacity=1, color = 'red',
               fillOpacity = 0.75, weight=2) %>%
  addPolylines(data=my_tracks$`125186_ds`,  opacity=1, color = 'red',
               fillOpacity = 0.75, weight=2) %>%
  addPolylines(data=my_tracks$`125186_us2`,  opacity=1, color = 'red',
               fillOpacity = 0.75, weight=2) %>%
  addAwesomeMarkers(lng = photo_metadata_site$lon_map,lat = photo_metadata_site$lat_map,
                    popup = popupImage(photo_metadata_site$url, src = "remote"),
                    clusterOptions = markerClusterOptions(),
                    label = paste0(photo_metadata_site$crossing_id, '_', photo_metadata_site$filename)) %>%
  addLayersControl(
    baseGroups = c("ESRI Aerial", "Topo"),
    # overlayGroups = c(my_tracks$`125000_ds_track`),
    options = layersControlOptions(collapsed = F)) %>% 
  
  addMiniMap(tiles = providers$"Esri.WorldTopoMap",
             zoomLevelOffset = -6)    # setView(lng = -105.644, lat = 51.618, zoom = 3) ##this becomes the latest and greatest pscis crossing utm
map
```



<br>

### Chuchinka-Table FSR {.tabset}


```{r}
##this is doing nothing right now
# my_site <- '125179'
#### Tributary to Missinka River - PSCIS 125179
```


```{r eval = FALSE}
photo_metadata_site <- photo_metadata %>% 
  filter(crossing_id %in% c('125247', '125253'))
```

<br>

```{r}
filter(table_overview_prep,
         Site %in% c('125247', '125253')) %>%
  select(-Comments) %>% 
  gt::gt() %>% 
  tab_header(title="Overview") %>%
  cols_width(
    # vars(Comments) ~ px(300),
    # vars(`Habitat Gain (km)`) ~ px(70),
    everything() ~ px(90)
  ) %>% 
  tab_options(table.font.size = 11) %>% 
  tab_footnote(
    footnote = 'Habitat gain modelled based on Fish Habitat Model with 22% gradient threshold for "fish habitat".',
    locations =  cells_column_labels(
      columns = vars(`Habitat Gain (km)`)))

```

<br>

```{r}
filter(table_hab_prep, 
       Site %in% c('125247', '125253')) %>%
  gt::gt() %>% 
  tab_header(title="Habitat Summary") %>% 
  cols_width(
    vars(Comments) ~ px(250),
    vars(`Substrate (dominant)`,`Substrate (subdominant)`) ~ px(75),
    vars(Location) ~ px(60),
    everything() ~ px(50)
  ) %>% 
  tab_options(table.font.size = 11) 

```


### Chuchinka-Colbourne FSR {.tabset}


```{r site125345}
my_site <- '125345'

#### Tributary to Missinka River - PSCIS 125180

```

```{r eval=FALSE}
photo_metadata_site <- photo_metadata %>% 
  filter(crossing_id == my_site)
```


```{r}
filter(table_overview_prep,
         Site == my_site) %>%
  select(-Comments) %>% 
  gt::gt() %>% 
  tab_header(title="Overview") %>%
  cols_width(
    # vars(Comments) ~ px(300),
    # vars(`Habitat Gain (km)`) ~ px(70),
    everything() ~ px(90)
  ) %>% 
  tab_options(table.font.size = 11) %>% 
  tab_footnote(
    footnote = 'Habitat gain modelled based on Fish Habitat Model with 22% gradient threshold for "fish habitat".',
    locations =  cells_column_labels(
      columns = vars(`Habitat Gain (km)`)))

```


```{r}
filter(table_hab_prep, Site == my_site) %>%
  gt::gt() %>% 
  tab_header(title="Habitat Summary") %>% 
  cols_width(
    vars(Comments) ~ px(250),
    vars(`Substrate (dominant)`,`Substrate (subdominant)`) ~ px(75),
    vars(Location) ~ px(60),
    everything() ~ px(50)
  ) %>% 
  tab_options(table.font.size = 11) 

```

<br>




```{r site125186, eval=FALSE}
my_site <- '125186'
#### Tributary to Missinka River - PSCIS 	125186
```


```{r eval=FALSE}
photo_metadata_site <- photo_metadata %>% 
  filter(crossing_id == my_site)
```

<br>

```{r eval=FALSE}
filter(table_overview_prep,
         Site == my_site) %>%
  select(-Comments) %>% 
  gt::gt() %>% 
  tab_header(title="Overview") %>%
  cols_width(
    # vars(Comments) ~ px(300),
    vars(`Habitat Gain (km)`) ~ px(70),
    everything() ~ px(60)
  ) %>% 
  tab_options(table.font.size = 11) %>% 
  tab_footnote(
    footnote = 'Habitat gain modelled based on Fish Habitat Model with 22% gradient threshold for "fish habitat".',
    locations =  cells_column_labels(
      columns = vars(`Habitat Gain (km)`)))

```

<br>

```{r eval=FALSE}
filter(table_hab_prep, Site == my_site) %>%
  gt::gt() %>% 
  tab_header(title="Habitat Summary") %>% 
  cols_width(
    vars(Comments) ~ px(250),
    vars(`Substrate (dominant)`,`Substrate (subdominant)`) ~ px(75),
    vars(Location) ~ px(60),
    everything() ~ px(50)
  ) %>% 
  tab_options(table.font.size = 11) 

```

<br>

```{r eval=FALSE, out.width= '100%'}
##--------lets map it-----------------------------------------------------------------------
##time to set the watershed code here
##pass it get the watershed boundaries. Dissolve boundaries and display semi-transparent.
##add a culvert measurements output table with all the usual photos
##georeference the upstream and downstream photos from the camera by cross-referencing the time to the gps.


map <- leaflet() %>%
  # leaflet(height=500, width=500) %>% 
  addTiles() %>%
  addMouseCoordinates(proj4 = 26910) %>% ##can't seem to get it to render utms yet
  
  addProviderTiles("Esri.WorldImagery", group = "ESRI Aerial") %>% 
  addProviderTiles("Esri.WorldTopoMap", group = "Topo") %>%
  # addMeasure() %>% 
  # setView(lng = -105.644, lat = 51.618, zoom = 3)
  addPolylines(data=my_tracks$`125186_ds`,  opacity=1, color = 'red',
               fillOpacity = 0.75, weight=2) %>%
  addPolylines(data=my_tracks$`125186_us2`,  opacity=1, color = 'red',
               fillOpacity = 0.75, weight=2) %>%
  addAwesomeMarkers(lng = photo_metadata_site$lon_map,lat = photo_metadata_site$lat_map,
                    popup = popupImage(photo_metadata_site$url, src = "remote"),
                    clusterOptions = markerClusterOptions(),
                    label = photo_metadata_site$filename) %>%
  addLayersControl(
    baseGroups = c("ESRI Aerial", "Topo"),
    # overlayGroups = c(my_tracks$`125000_ds_track`),
    options = layersControlOptions(collapsed = F)) %>% 
  
  addMiniMap(tiles = providers$"Esri.WorldTopoMap",
             zoomLevelOffset = -6)    # setView(lng = -105.644, lat = 51.618, zoom = 3) ##this becomes the latest and greatest pscis crossing utm
map
```



## Overview Map

```{r eval=TRUE, out.width= '100%'}
##--------lets map it-----------------------------------------------------------------------
##time to set the watershed code here
##pass it get the watershed boundaries. Dissolve boundaries and display semi-transparent.
##add a culvert measurements output table with all the usual photos
##georeference the upstream and downstream photos from the camera by cross-referencing the time to the gps.

loadd(tracks, photo_metadata)
map <- leaflet() %>%
  leaflet(height=500, width=780) %>% 
  addTiles() %>%
  addMouseCoordinates(proj4 = 26910) %>% ##can't seem to get it to render utms yet
  
  addProviderTiles("Esri.WorldImagery", group = "ESRI Aerial") %>% 
  addProviderTiles("Esri.WorldTopoMap", group = "Topo") %>%
  # addMeasure() %>% 
  # setView(lng = -105.644, lat = 51.618, zoom = 3)
  addPolylines(data=tracks,  opacity=1, color = 'red',
               fillOpacity = 0.75, weight=2) %>%
  # addPolylines(data=my_tracks$`125180_us`,  opacity=1, color = 'red',
  #              fillOpacity = 0.75, weight=2) %>%
  addAwesomeMarkers(lng = photo_metadata$lon_map,lat = photo_metadata$lat_map,
                    popup = popupImage(photo_metadata$url, src = "remote"),
                    clusterOptions = markerClusterOptions(),
                    label = paste0(photo_metadata$crossing_id, '_', photo_metadata$filename)) %>%
  addLayersControl(
    baseGroups = c("ESRI Aerial", "Topo"),
    # overlayGroups = c(my_tracks$`125000_ds_track`),
    options = layersControlOptions(collapsed = F)) %>% 
  
  addMiniMap(tiles = providers$"Esri.WorldTopoMap",
             zoomLevelOffset = -6)    # setView(lng = -105.644, lat = 51.618, zoom = 3) ##this becomes the latest and greatest pscis crossing utm
map
```

## Workflow Layout
This project is in the early stages of active development, is incomplete, may contain errors and is expected to change substantially. It has been made available for stakeholder engagement and to facilitate discussion regarding potential fish passage restoration candidates.  Please contact al@newgraphenvironment.com (2507771518) with any questions or concerns.  

<br>

 * Code and data for the workflow is available at [New Graph Environment Github Site ](https://github.com/NewGraphEnvironment/Parsnip_Fish_Passage).  This report is generated from scratch from a Rmarkdown document processing raw data from populated:

    + [Fish Data Submission Spreadsheet Template - V 2.0, April 16, 2019 ](https://www2.gov.bc.ca/gov/content/environment/plants-animals-ecosystems/fish/fish-and-fish-habitat-data-information/fish-data-submission/submit-fish-data#submitfish) 

    + [pscis_assessment_template_v23.xls](https://www2.gov.bc.ca/gov/content/environment/natural-resource-stewardship/land-based-investment/investment-categories/fish-passage/assessment-projects)


    + Excel spreadsheet with priority level detailed for each of the crossings surveyed.

    + GPS tracks and points from field surveys.  

    + Photos and photo metadata.  When not available in metadata photos georeferenced by aligning photostamp time with GPS track times.

<br>


```{r out.width = '100%'}
plot
```

